---
title: "Lab 04 - Data Type Coercion"
author: "chris serrano"
date: "3/7/23"
output: html_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
library(openintro)
```

## Exercises

### Exercise 1


-   Vector `c(1, 1L, "C")`

```{r echo = F}
1
1L
"C"
```
 1 is a `r typeof(1)`, 1L is an `r typeof(1L)`, C is a `r typeof("C")`.
```{r echo = F}
c(1, 1L, "C")
```
The output of the second code chunk is a vector.
```{r echo = F}
(c(1, 1L, "C"))
```
all the variables are characters.
### Exercise 2

Remove this text, and add your answer for Exercise 2 here.

### Exercise 3

Remove this text, and add your answer for Exercise 3 here.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

### Exercise 9

Remove this text, and add your answer for Exercise 9 here.

### Exercise 10

Remove this text, and add your answer for Exercise 9 here.
